---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# histogramplot

<!-- badges: start -->
<!-- badges: end -->

 This package is used for data visualization, especially when there is
    a group variable in a dataset. It contains the function histogram_plot
    that can make histogram plots for a certain variable 
    in different groups or levels in the dataset seperately.

## Installation

You can install the released version of histogramplot from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("histogramplot")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("graceyin06/545B-package")
```

### Required packages for applying the function "histogram_plot" in histogramplot package 
* magrittr
* dplyr
* tidyverse

## Example

There are two examples showing how to use this package to make seperate histogram plots.

```{r}
#load the required packages
suppressMessages(library(dplyr))
suppressMessages(library(magrittr))
suppressMessages(library(datateachr))
suppressMessages(library(tidyverse))
```

### Example 1
Make the histogram plots for radius_mean in two diagnosis groups.

```{r}
#load the dataset
library(gapminder)
#load the histogramplot package
library(histogramplot)
## basic example code
# make two histogram plots for radius_mean in two diagnosis groups.
histogram_plot(cancer_sample,diagnosis,radius_mean,"radius_mean")
```

### Example 2

Make the histogram plots for lifeExp in five continents in gapminder datset
.
```{r}
### make the histogram plots for lifeExp in five continents.
histogram_plot(gapminder,continent,lifeExp,"lifeExp")
```
